Chinese Poem Generator from Image

### 2015-12-01 paper.tex
finish

%%%%%%%%% ABSTRACT
\begin{abstract}
   	Chinese poem is very popular in China, for it's meaningful, convenience and gentle. It is very common in China that children can recite lot's of poems before primary school. 
	In Chinese parmary school, most Chinese teacher will teach children how to make sentences based on what they look. In addition, it's a way to cultivate the ability of communication for children.

@@

In this paper, we will develop a generative models that can recognize the image, extract the feature in the image, and generate the poem based on the image. This is very basic for people, but hard for computer. In some sense, we want to explore the ability of computer.
%-------------------------------------------------------------------------
\subsection{Problem Statement}
This problem is a generative problem. The generative models should generate the poem that base on an specific image, which means that the poem should describe the image. For this purpose, the input image must contains some information and people can easily find out what the emotion it convey. The graph contains with different emotion is best for both people and computer to create the poem.

The output should be the beautiful poem that it's meaning is closed to this image.

\section{Related Work}
	Generating poem is popular in recent years, and there are many people research on it. On the other hand, explain image with sentence has also made great progress after deep learning widely used. Our approach is a combination of above two aspects, we select two methods that performing well in corresponding aspects, and try to get a fantastic result.
\section{Plan}
\subsection{Image to Sentence}
The first part of this problem is to generate a sentence based on the image. This sentence must contain the detail of this image, and it can describe this image.

The method we want to use here is proposed by Junhua Mao\footnote{ Junhua Mao, Wei Xu, Yi Yang, Jiang Wang, Alan L. Yuille : Explain Images with Multimodal Recurrent Neural Networks.}. We use a multimodal Recurrent Neural Networks (m-RNN) model to address both the task of generating novel sentences descriptions for images, and the task of image and sentence retrieval. The whole m-RNN architecture contains a language model part, an image part and a multimodal part. The language model part learns the dense feature embedding for each word in the dictionary and stores the semantic temporal context in recurrent layers. The image part contains a deep Convulutional Neural Network (CNN) \footnote{A. Krizhevsky, I. Sutskever, and G. E. Hinton. Imagenet classification with deep convolutional neural networks. In NIPS, pages 1097–1105, 2012.} which extracts image features.

@@

\subsubsection{Poem generator}
	The method we will use to generate poem is proposed by Mirella Lapata\footnote{Xingxing Zhang, Mirella Lapata : Chinese Poetry Generation with Recurrent Neural Networks.}.First, to create the first line of poem, We select all phrases corresponding to the users’s keywords and generate all possible combinations satisfying the tonal pattern constraints. We use a language model to rank the generated candidates and select the best ranked one as the first line in the poem. In implementation, we employ a character-based recurrent neural network language model.
	And after that, we generate the rest poem lines with original lines. Convert lines $s_1$...$s_i$ into vectors $v_1$...$v_i$ with a convolutional sentence model (CSM). Next, a recurrent context model (RCM) takes $v_1$...$v_i$ as input and outputs $u_{j,i}$.Finally, $u_{1,i}$, $u_{2,i}$,...,$u_{j,i}$ and the first $j$ characters $w_1$...$w_j$ in line $s_{i+1}$ serve as input to a recurrent generation model (RGM) which estimates $P(w_{j+1} = k | w_{1:j} ,s_{1:i} )$ with $k\in V$, the probability distribution of the $j+1$ th character over all words in the vocabulary $V$.
%-------------------------------------------------------------------------
\section{Dataset}
The dataset we used is IAPR TC-12 dataset, which used to training the model that explain image. The other is Chinese Poetry corpus.
\section{Intermediate Result}
We have built a temporary framework and consulted one expert about this problem. The expert thought it's a very good idea and gave some advices.
We will soon try to use theano to implement our idea, for this week is the deadline of building a cpu.
\end{document}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
   	Chinese poem is very popular in China, for it's meaningful, outstanding and gentle. It is very common in China that children can recite lot's of poems before primary school. As a part of language, poem can represent the Chinese culture totally. 
	In Chinese primary school, most Chinese teachers will teach children how to make sentences based on what they look. In addition, it's a way to cultivate the ability of communication for children.

@@

In this paper, we will develop a generative model that can recognize the image, extract the features in the image, and generate the poem based on the image. This is very basic for people, but hard for computer. In some sense, we want to explore the speaking ability of computer.
%-------------------------------------------------------------------------
\subsection{Problem Statement}
This problem is a generative problem. The generative model should generate the poem that base on an specific image, which means that the poem should describe the image.

For this purpose, the input image must contains some information and people can easily find out what the emotion it convey. The graph contains with different emotion and things is best for both people and computer to create the poem.

The output should be the beautiful poem that it's meaning is closed to this image. There are also some standards to judge whether the poem is good or not. The standard includes the atmosphere contained in the poem, and the meaning of the poem. Sounds of the poem is another factor which influence the performance a lot.

\section{Related Work}
	Generating poem is popular in recent years, and there are many people research on it. On the other hand, explaining image with sentence has also made great progress after deep learning widely used. Our approach is a combination of above two aspects, we select two methods that performing well in corresponding aspects, and try to get a fantastic result.
\section{Plan}
\subsection{Image to Sentence}
The first part of this problem is to generate a sentence based on the image. This sentence must contain the detail of this image, and it can describe this image.

The method we want to use here is proposed by Junhua Mao\footnote{ Junhua Mao, Wei Xu, Yi Yang, Jiang Wang, Alan L. Yuille : Explain Images with Multimodal Recurrent Neural Networks.}. We use a multimodal Recurrent Neural Networks (m-RNN) model to address both the task of generating novel sentences descriptions for images, and the task of image and sentence retrieval. The whole m-RNN architecture contains a language model part, an image part and a multimodal part. The language model part learns the dense feature embedding for each word in the dictionary and stores the semantic temporal context in recurrent layers. The image part contains a deep Convolutional Neural Network (CNN) \footnote{A. Krizhevsky, I. Sutskever, and G. E. Hinton. Imagenet classification with deep convolutional neural networks. In NIPS, pages 1097–1105, 2012.} which extracts image features.

@@

\subsection{Poem generator}
	The method we will use to generate poem is proposed by Mirella Lapata\footnote{Xingxing Zhang, Mirella Lapata : Chinese Poetry Generation with Recurrent Neural Networks.}.First, to create the first line of poem, We select all phrases corresponding to the users’s keywords and generate all possible combinations satisfying the tonal pattern constraints. We use a language model to rank the generated candidates and select the best ranked one as the first line in the poem. In implementation, we employ a character-based recurrent neural network language model.
	And after that, we generate the rest poem lines with original lines. Convert lines $s_1$...$s_i$ into vectors $v_1$...$v_i$ with a convolutional sentence model (CSM). Next, a recurrent context model (RCM) takes $v_1$...$v_i$ as input and outputs $u_{j,i}$.Finally, $u_{1,i}$, $u_{2,i}$,...,$u_{j,i}$ and the first $j$ characters $w_1$...$w_j$ in line $s_{i+1}$ serve as input to a recurrent generation model (RGM) which estimates $P(w_{j+1} = k | w_{1:j} ,s_{1:i} )$ with $k\in V$, the probability distribution of the $j+1$ th character over all words in the vocabulary $V$.
%-------------------------------------------------------------------------
\section{Dataset}
The dataset we used is IAPR TC-12 dataset, which used to training the model that explain image.

The other is Chinese Poetry corpus to train for the generate part.
\section{Intermediate Result}
We have built a temporary framework and consulted one expert about this problem. The expert thought it's a very good  and practical reasonable idea and gave some advices.
We will soon try to use theano to implement our idea. Recent three weeks is the deadline of building a cpu so we don't have enough time to try our idea.
\end{document}
